README

### 2017-04-13 src/README.Rmd
Retrieve article citations using R, merge with notes

>>>>

# Joining articles with assignees
The articles were searched for and DOIs were saved in a CSV file with notes related to the articles and selections. Using this CSV file retrieve the BibTex citations for those available and write a "Assigned_Articles.bib" file to disk as well as the updated "Assigned_Articles.csv".

```{r join_files, warning=FALSE}
notes <- read.csv("Assigned_article_notes.csv", strip.white = TRUE)

bib <- RefManageR::GetBibEntryWithDOI(notes$doi)

# Join articles and references for saving to CSV for reference
Assigned_Articles <- dplyr::left_join(as.data.frame(bib), notes, by = "doi")

write.csv(Assigned_Articles, "Assigned_Articles.csv")

RefManageR::WriteBib(bib, "Assigned_Articles.bib")

Note that not all of the articles have DOIs and some of the DOIs don't appear to work, so we'll manually add them here.

```{r add_missing_articles}
